Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
punctuation at the end of footnote

Our results on the public part of the DCASE 2016 dataset are reported in Table \ref{table:dcase2016}, compared with a baseline using MFCCs and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. This baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes on the public part is brought from $70.8\%$ to $79.4\%$\footnote{Challenge results on the private part of the dataset are expected to be published in August 2016}.
Furthermore, our cross-validation analyses confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.

>>>>

Our results on the public part of the DCASE 2016 dataset are reported in Table \ref{table:dcase2016}, compared with a baseline using MFCCs and a generative classifier, namely Gaussian mixture models with $16$ Gaussians per model. This baseline relies on a late integration scheme, wherein the reduction function $\rho$ is a product of likelihoods.
The average accuracy across classes on the public part is brought from $70.8\%$ to $79.4\%$\footnote{Challenge results on the private part of the dataset are expected to be published in August 2016.}.
Furthermore, our cross-validation analyses confirmed that the value $T=372\,\mathrm{ms}$ for the support of the low-pass filter $\boldsymbol{\phi}(t)$ is optimal when applying late integration by majority voting.
